---
title: "Writing Reports with R Markdown"
output: html_document
date: "2023-04-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Here I use and message=FALSE adn warning = FALSE to hide the message lines. 
```{r import data and libraries , message=FALSE, warning=FALSE}
OilWomen<-read.csv('https://raw.githubusercontent.com/hknd23/PLSC-309-SP23/main/Data/oilwomen.csv')
library(devtools)
install_github('hknd23/MarginalEffectsPlots')
library(MarginalEffectsPlots)
library(stargazer)
```

## R Markdown
In this study, I want to look at the effect of economic growth, oil exports, and having Islam as major religion on women representation. 

First, I notice that GDP per capita is right-skewed, so I take the logarithm of the variable so that it looks "normal":

```{r log}
hist(OilWomen$gdpcap2000)
OilWomen$logGDP<-log(OilWomen$gdpcap2000)
hist(OilWomen$logGDP)

```


Now, I want to look at the descriptive statistics of my main variables

```{r descriptives}
summary(OilWomen[,c('female_seats','polity','oil','zislam','logGDP','gdpcap2000','PR')])
```

## Including Plots

Third, I use some visualization to show some data trends

```{r plots}
hist(OilWomen$female_seats)
barplot(table(OilWomen$zislam))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r scatterplot, echo=FALSE}
plot(OilWomen$polity,OilWomen$female_seats,xlab = "Polity",ylab = "Female Seats")
abline(lm(female_seats~polity,data=OilWomen))
```

I now want to run two linear regression models: 

```{r linear models}
model2<-lm(female_seats~logGDP+polity+oil,data=OilWomen)
model3<-lm(female_seats~polity+oil+zislam*logGDP+PR,data=OilWomen)
summary(model2)
summary(model3)

```

With an interaction term, let's use the plotting functions to interpret them more easily

```{r marginal effects}
meggplot(model3,'logGDP','zislam')
meggplot(model3,'zislam','logGDP')
```

After I'm done writing the report, I can use File > Knit Document to produce my report.
